---
title: "Dashboard"
format:
  html:
    grid:
      body-width: 1400px
    theme:
      - Minty
      - style.css
    toc: true
    toc-depth: 5
filters:
  - quarto
---

```{r}
#| label: globals
#| include: false

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
data_directory_path <- here::here("communication", "dashboard", "data")

url_css <- "https://www.dropbox.com/scl/fi/hca7tog3830ir7ro9fszt/styles.css?rlkey=pma97454kb75qzuj9znv86zrf&dl=1"
url_references <- "https://www.dropbox.com/scl/fi/n7t8g3hn32d8e5gf2rcti/references.bib?rlkey=xy251n44q3y0t3omxpqk0dvyf&dl=1"
file_css <- "style.css"
file_references <- "references.bib"
urls <- c(url_css, url_references)
files <- c(file_css, file_references)

purrr::walk2(urls, files, ~download.file(.x, .y))
```

## Descriptive statistics

### Book data

This table shows descriptive statistics for the variables available in the main book data dataset. These are compiled including only firms that match those in the price dataset (`AGMdata.dta`). Are further excluded firm-year combinations that fail the "amount verification" for total assets and total liabilities as well as missing or "0" records. 


```{r}
#| label: book-stats-load

descriptive_stats_book_by_reporting_frequency_data_path <- 
  file.path(data_directory_path, "descriptive-statistics", "book", "statistics-by-reporting-frequency.rds")

book_stats <- readr::read_rds(descriptive_stats_book_by_reporting_frequency_data_path)
```

```{r}
#| label: book-stats-table

kableExtra::kable(
  book_stats, align = c(rep("l", 4L), rep("r", 6L)), format.args = list(big.mark = " ")
  ) |> 
  kableExtra::column_spec(1L:4L, bold = TRUE) |> kableExtra::column_spec(5L:10L, color = "#4285f4") |>
  kableExtra::collapse_rows(1L:3L, valign = "top") |>
  kableExtra::kable_styling(bootstrap_options = "hover")
```

```{r}
#| label: book-stats-download

downloadthis::download_this(
  book_stats,
  output_name = "Book data - descriptive statistics",
  output_extension = ".csv",
  button_label = "Download data as csv",
  button_type = "default",
  has_icon = TRUE,
  icon = "fa fa-save"
  )
```
